\documentclass[letterpaper,11pt]{article}
\usepackage[pagesetup]{tucv}

% Footer test123
%\fancyfoot[C]{Nathan Buckner - Page \thepage}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Nathan Buckner} & (210) 396-8151 \\
 & bucknerns@gmail.com \\
\end{tabular*}

\resheading{Objective}
\begin{itemize}
    \item[]
        \resentrysinglecol{
            Detail-oriented, highly motivated Senior Software Engineer with a passion for learning and making an impact.
            Exceptional design, debugging, testing, problem solving and critical thinking.
            Searching for a company that I can be an $\int$ part, culturally and intellectually.}
\end{itemize}

\resheading{Recent Employment}
\begin{itemize}
% Employment Format
    % \item[]
    %     \resemployer[Brief description of employer]{Employer name}{Location}
    %         \resjob[Description of job]{Job title}{Start}{End}
    \item[]
        \resemployer{Roku}{San Jose}
            \resjob[
                Worked as a technical lead for the team.
                Wrote internal event collection, payment provideo event collection services.
                Created EMR pipelines for transforming and publish service events to data warehouse.
                Migrated PCI data to new payment provider.
                Wrote, packaged and setup CI pipelines for testing framework.
                ]{Senior Software Engineer}{June 2018}{Present}
        \resemployer{Amazon - Lab126}{Sunnyvale}
            \resjob[
                Designed and implemented a test framework to replace organically grown FireTV test framework.
                Designed page object model navigation library for FireTV testing.
                Conducted train effort for local and overseas employees in person.
                ]{Senior Software Developer L5,L6(promoted in June 2018)}{May 2017}{June 2018}
        \resemployer{Rackspace - the \#1 managed cloud company}{San\,Antonio}
            \resjob[
                Built clients and behaviors to facilitate Rackspace to AWS migrations.
                Creating complex deployments and test scenarios for migrations.
                Created metrics API backed by object storage with ELK stack dashboard.
                Designed test harness for software defined networks.
                Capacity dashboard (Flask/Angular).
                Billing Testing Automation.
                Onboarding class for new hires.
                Threat Models, Code reviews, infrastructure/web app pen-testing.
                ]{Software Developer/Security Developer in Test II-IV}{July 2013}{Feb 2017}
\end{itemize}

% \resheading{Conferences}
% \begin{itemize}
%     % \item[] \resconference{Lascon}{Speaker (2015)}
%     %     \ressubconference{OpenStack API Security Testing Automation in Action}{Speaker (2014)}
%     \item[] \resconference{Lascon}{Speaker (2014, 2015)}
% \end{itemize}


\resheading{Skills}
\begin{itemize}
    \item []
        \resdesc{Languages:}{Python, Java, Shell/Bash, Memes}
        \resdesc{Databases:}{DynamoDB, Redis, SQL databases + ORMs, MongoDB}
        \resdesc{Web:}{Spring Boot, Flask, Falcon, Requests, Protobuf, Fastapi, Json, Avro}
        \resdesc{Cloud/Virtualization:}{AWS, Openstack, Docker, Terraform, ECS, EC2}
        \resdesc{CI/CD+Tools:}{Gitlabci, Jenkins, Git, Tox, Unittest, Checkstyle, Junit, Gerrit, Gradle, Pip}
\end{itemize}

\resheading{Education}
\begin{itemize}
% Education Item Format
    % \item[]
    %     \resschool[Notes about school]{School Name}{Location}
    %         \resdegree[degree notes]{Degree}{Major}{Date}
    %         \ressubentry{Certificate, etc.}{Date}
    \item[]
        \resschool{University of Texas}{San\,Antonio}
            \resdegree[Concentration in Security]{Bachelor's}{Computer Science}{}
\end{itemize}

\resheading{Links}
\begin{itemize}
    \item[]
        \resdesc{Github:}{https://github.com/bucknerns}
        \resdesc{LinkedIn:}{/}
\end{itemize}

%\footnotetext[1]{Denotes a peer-reviewed publication}
% \resheading{Publications and Presentations}
% \begin{itemize}
% % This item provides article title (bolded) and rest-of-citation fields.
% %\item[] \resbib{``Article title''\footnotemark[1]}{Paper at Conference, Year. Authors.}
% \end{itemize}

\end{document}
